---
title: "Appex 14 - Group 9"
format: 
  html:
    self-contained: true
editor: visual
---

## Part 1

Run the code below to create your dataset:

```{r}
library(tidyverse)
set.seed(31)
n <- 10000
data <- tibble(
    x1 = rnorm(n),
    x2 = rnorm(n),
    x3 = rnorm(n),
    x4 = rnorm(n),
    x5 = rnorm(n),
    x6 = rnorm(n),
    x7 = rnorm(n),
    x8 = rnorm(n),
    x9 = rnorm(n),
    x10 = rnorm(n),
    x11 = rnorm(n),
    x12 = rnorm(n),
    x13 = rnorm(n),
    x14 = rnorm(n),
    x15 = rnorm(n),
    x16 = rnorm(n),
    x17 = rnorm(n),
    x18 = rnorm(n),
    x19 = rnorm(n),
    x20 = rnorm(n),
    y = 0.2 * x1 + 0.2 * x2 + 0.2 * x3 + rnorm(n)
  )
```

Run the code to fit a linear model predicting `y` using all of the other predictors.

```{r}
full_model <- lm(y ~ ., data = data) 
summary(full_model)
```

If you were only selecting variables based on statistical significance, what would you include?

## Part 2

Update the code below to use the `regsubset` function to find the best subset of variables to include in your model with `BIC` as the criterion.

```{r}
# install.packages("leaps")
library(leaps)
all_subsets <- regsubsets(---)
plot(all_subsets)
```

Which variables did you choose?

